---
title: "Vaghani_D_12"
output:
  html_document: default
  word_document: default
---

# Task 1
```{r}
#Installing Mongodb Server on system.
#see the steps in attached image with this assignment.

```


#Task 2
```{r}
Birdstrikes <- read.csv("BirdStrikes.csv")
mongoBirdstrikes <- mongo("Birdstrikes")
mongoBirdstrikes$insert(Birdstrikes)
```
#[OUTPOUT]
Complete! Processed total of 99405 rows.
$nInserted
[1] 99405

```{r}
mongoBirdstrikes$export(file("data.txt"))
```
#[OUTPUT]
[output]
Done! Exported a total of 99405 lines.



#Task 3A Distinct Airport Names
```{r}
mongoBirdstrikes$distinct("AirportName")
```
#[OUTPUT]
head(mongoBirdstrikes$distinct("AirportName"))

[1] "NEWARK LIBERTY INTL ARPT"          "UNKNOWN"                          
[3] "DENVER INTL AIRPORT"               "CHICAGO O'HARE INTL ARPT"         
[5] "JOHN F KENNEDY INTL"               "CINCINNATI MUNI ARPT-LUNKEN FIELD"



#Task 3B Count with origin state = New Jersey
```{r}

Jersey <- mongoBirdstrikes$count('{"OriginState":"New Jersey"}')
```
#[OUTOPUT]
head(Jersey)
[1] 2936


#Task 3C Getting data with conditions=Fog and has fields like Record ID in desceding order.
```{r}

fog <- mongoBirdstrikes$find('{"ConditionsPrecipitation":"Fog"}', sort= '{"RecordID":-1}')
```
#[OUTPUT]
head(fog)
  AircraftType                  AirportName Altitudebin AircraftMakeModel WildlifeNumberstruck
1     Airplane            REDDING MUNICIPAL   > 1000 ft           EMB-120                    1
2     Airplane            HEATHROW - LONDON   < 1000 ft             A-330              2 to 10
3     Airplane             ADAMS FIELD ARPT   > 1000 ft          CL-RJ900                    1
4     Airplane GEORGE BUSH INTERCONTINENTAL   < 1000 ft           EMB-145              2 to 10
5     Airplane          JOHN F KENNEDY INTL   < 1000 ft         B-737-800            11 to 100
6     Airplane              SACRAMENTO INTL     Unknown      CL-RJ100/200                    1
  EffectImpacttoflight EffectOther LocationNearbyifenroute AircraftFlightNumber    FlightDate
1                 None                                                          12/30/11 0:00
2                 None                                                           12/6/10 0:00
3                                                                          2681 12/13/11 0:00
4                 None                                                    4672? 12/31/11 0:00
5                 None                                                     1850  12/5/11 0:00
6                 None                                                     4562 11/29/11 0:00


#Task 3D Fetch columns for AircraftAirlineOperator with certain columns.
```{r}

AAirlines<- mongoBirdstrikes$find('{"AircraftAirlineOperator":"AMERICAN AIRLINES"}', fields = '{"RecordID":1, "OriginState":1, "AircraftAirlineOperator":1, "AirportName":1}')
```
Imported 3851 records. Simplifying into dataframe...

#[OUTPUT]
head(AAirlines)
                       _id                 AirportName RecordID AircraftAirlineOperator OriginState
1 58432f8f49f3ee01971d4e77                     UNKNOWN   204787       AMERICAN AIRLINES         N/A
2 58432f8f49f3ee01971d4e86        MINETA SAN JOSE INTL   208470       AMERICAN AIRLINES  California
3 58432f8f49f3ee01971d4e9d         JOHN F KENNEDY INTL   202568       AMERICAN AIRLINES    New York
4 58432f8f49f3ee01971d4ea5 DALLAS/FORT WORTH INTL ARPT   200470       AMERICAN AIRLINES       Texas
5 58432f8f49f3ee01971d4eb3         JOHN F KENNEDY INTL   202957       AMERICAN AIRLINES    New York
6 58432f8f49f3ee01971d4ed4        SANTO DOMINGO/LAS AM   200801       AMERICAN AIRLINES         N/A
```{r}
CONAirlines<- mongoBirdstrikes$find('{"AircraftAirlineOperator":"CONTINENTAL AIRLINES"}', fields = '{"RecordID":1, "OriginState":1, "AircraftAirlineOperator":1, "AirportName":1}')
```

Imported 833 records. Simplifying into dataframe...

#[OUTPUT]
head(CONAirlines)
                       _id              AirportName RecordID AircraftAirlineOperator OriginState
1 58432f8f49f3ee01971d4e71 NEWARK LIBERTY INTL ARPT   200508    CONTINENTAL AIRLINES  New Jersey
2 58432f8f49f3ee01971d4e8a  LAFAYETTE REGIONAL (LA)   204764    CONTINENTAL AIRLINES   Louisiana
3 58432f8f49f3ee01971d4f31                  UNKNOWN   208539    CONTINENTAL AIRLINES         N/A
4 58432f8f49f3ee01971d4fc2                  UNKNOWN   205201    CONTINENTAL AIRLINES         N/A
5 58432f8f49f3ee01971d5069 NEWARK LIBERTY INTL ARPT   202226    CONTINENTAL AIRLINES  New Jersey
6 58432f8f49f3ee01971d5089                  UNKNOWN   202964    CONTINENTAL AIRLINES         N/A



